\documentclass[11pt,a4paper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{array}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{xcolor}

\definecolor{flyticsblue}{RGB}{0,51,102}

\title{\textbf{Feasibility Analysis\\AI-Enhanced Client Services Platform}}
\author{Prepared for Flytics Client Services Business Unit}
\date{May 2026}

\begin{document}

\maketitle

\section*{Executive Position}

The Flytics Client Services Platform is feasible if delivery is phased around a reliable core marketplace engine before advanced AI automation is treated as a dependency for revenue. The project has a strong business rationale because it turns a manual service operation into a scalable request, assignment, analytics, and billing workflow. The highest feasibility risks are pilot supply density, regulatory compliance, data governance for imagery, AI quality control, and integration complexity across payments, storage, weather, airspace, and analytics services.

\section{Feasibility Summary}

\begin{longtable}{>{\bfseries}p{0.22\textwidth}p{0.18\textwidth}p{0.48\textwidth}}
\toprule
Dimension & Rating & Rationale \\
\midrule
Business feasibility & High & Client demand can be served without client-owned drone assets, and the marketplace model supports recurring monitoring, premium analytics, and priority services. \\
Technical feasibility & Medium-High & Core portal, workflow, storage, billing, and matching capabilities are standard web platform patterns; large-file analytics, geospatial constraints, and AI governance require disciplined architecture. \\
Operational feasibility & Medium & Success depends on pilot onboarding, credential verification, local coverage, quality control, support workflows, and clear escalation paths. \\
Legal and compliance feasibility & Medium & Drone operations, airspace authorization, insurance, privacy, and client data rights must be encoded into workflow checks and contracts. \\
Schedule feasibility & Medium & A 12-month delivery window is achievable for a staged launch if Phase 1 focuses on minimum viable operations and AI features are introduced progressively. \\
Financial feasibility & Medium-High & Revenue potential is credible, but margin must be validated against pilot payouts, cloud storage, AI processing, support, acquisition, and compliance costs. \\
\bottomrule
\end{longtable}

\section{Business Feasibility}

The platform addresses a clear gap: clients need drone data and analysis without owning aircraft, staffing pilots, or managing compliance. Flytics can differentiate by combining a qualified pilot network, guided client intake, consistent deliverables, and AI-assisted analytics.

\subsection*{Feasible Value Drivers}

\begin{itemize}[leftmargin=*]
    \item Faster conversion from web inquiry to scoped service request.
    \item Higher pilot utilization through centralized work distribution.
    \item More consistent pricing through configured price corridors and bid comparison.
    \item Increased average order value from analytics add-ons, report packages, and priority service.
    \item Repeat revenue from monitoring subscriptions and enterprise account workflows.
\end{itemize}

\subsection*{Business Conditions for Success}

\begin{itemize}[leftmargin=*]
    \item Minimum regional pilot coverage must be defined before market launch.
    \item Service packages must be standardized enough for quoting, delivery, and reporting.
    \item Operations must retain override authority for pricing, assignment, compliance, and client deliverables.
    \item Revenue projections must be validated with customer interviews, pricing tests, and pilot payout assumptions.
\end{itemize}

\section{Technical Feasibility}

The recommended architecture is a modular web platform with a core domain engine, separate user experiences for clients, pilots, and internal teams, and asynchronous processing for imagery and analytics.

\begin{longtable}{>{\bfseries}p{0.28\textwidth}p{0.58\textwidth}}
\toprule
Component & Feasibility assessment \\
\midrule
Client portal & Feasible with standard account, request intake, file upload, quote review, deliverable download, and messaging patterns. \\
Pilot portal & Feasible with onboarding, credential upload, availability, bid submission, assignment acceptance, mission updates, and payout visibility. \\
Operations console & Feasible but must be prioritized early because it controls exceptions, compliance review, quality assurance, and support. \\
Core engine & Feasible if domain rules are explicit, testable, and isolated from external providers. This is the most important engineering foundation. \\
AI services layer & Feasible as recommendation and extraction services. It should not be the sole authority for eligibility, pricing, assignment, or compliance. \\
Analytics pipeline & Feasible with asynchronous jobs, object storage, metadata tracking, review queues, and model output versioning. \\
Integrations & Feasible but risky if introduced too broadly. Payments, storage, identity, notifications, weather, and airspace should use adapter boundaries. \\
\bottomrule
\end{longtable}

\section{Core Engine Feasibility Requirements}

The core engine is feasible when implemented as a deterministic domain layer with explicit state, rules, and events. It should provide:

\begin{enumerate}[leftmargin=*]
    \item A canonical mission lifecycle with valid state transitions and rejection reasons.
    \item Eligibility rules that can run without AI provider availability.
    \item Pricing rules that separate base pricing, AI guidance, pilot bids, discounts, platform fees, and approvals.
    \item Assignment logic that separates hard filters from ranking scores.
    \item Event records for every business action affecting request status, quote, bid, assignment, deliverable, invoice, payout, or subscription.
    \item Adapter interfaces for identity, payment, storage, weather, airspace, maps, notifications, AI providers, and accounting.
    \item Automated tests for state transitions, permission checks, pricing calculations, bidding windows, pilot eligibility, and billing events.
\end{enumerate}

\section{Operational Feasibility}

Operational feasibility depends on Flytics treating the platform as a managed service operation, not only a software product. Internal teams need tools for request review, pilot qualification, exception handling, client communication, service quality, and billing reconciliation.

\begin{longtable}{>{\bfseries}p{0.24\textwidth}p{0.30\textwidth}p{0.34\textwidth}}
\toprule
Operational area & Feasibility risk & Required control \\
\midrule
Pilot onboarding & Invalid or expired certifications, insurance gaps, inconsistent equipment data & Credential workflow, expiration alerts, manual approval, and audit records \\
Mission execution & Weather, airspace, client site constraints, access issues, failed flights & Pre-flight risk checks, mission status updates, cancellation rules, and rescheduling workflow \\
Deliverable quality & Inconsistent imagery, incomplete analysis, client disputes & Quality review queue, deliverable checklist, report templates, and rework tracking \\
Support & Client and pilot questions during active missions & Ticket or message history linked to request and mission records \\
Finance & Payment failures, payout disputes, subscription changes & Billing event ledger, reconciliation views, and manual adjustment controls \\
\bottomrule
\end{longtable}

\section{Legal, Compliance, and Data Feasibility}

The project is feasible only if compliance requirements are embedded into the workflow from the first release. The platform should capture pilot certification and insurance status, maintain client authorization records, support airspace and weather checks, and preserve audit trails for business decisions.

Drone imagery can include sensitive site, infrastructure, location, and client operational data. The system must define access control, storage region, retention, sharing, deletion, and contract terms before production launch. AI model outputs must be labeled as generated or assisted analysis when appropriate and reviewed before high-impact client delivery.

\section{Financial Feasibility}

The revenue model supports continued investment, but it is not sufficient by itself to approve full-scale development. A margin model must be produced before Phase 2 completion. The model should include pilot payouts, payment processing, cloud storage, AI inference and training costs, support labor, sales and marketing, insurance, compliance administration, and rework.

\section{Feasibility Decision}

The project should proceed using a phased delivery approach.

\begin{longtable}{>{\bfseries}p{0.24\textwidth}p{0.64\textwidth}}
\toprule
Decision & Proceed with controlled phased implementation. \\
Primary condition & Launch the core marketplace workflow and operations controls before relying on advanced AI automation. \\
Phase 1 gate & Client intake, pilot onboarding, eligibility, bidding, assignment, storage, notifications, operations console, billing trigger, and audit logging are working end to end. \\
Phase 2 gate & AI services improve intake, matching, pricing, and risk scoring while remaining reviewable and overridable. \\
Phase 3 gate & Analytics products, subscriptions, dashboards, and scale targets are validated by real usage, margin, and quality metrics. \\
\bottomrule
\end{longtable}

\end{document}
